Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-09-13 psy_peds.Rmd
read the most updated ICD file codes

```{r}
icdCodes <- read.csv("public-data/pediatric_psychiatric_ICD10_codes.csv", header = TRUE, colClasses = "character") %>% 
  rename(disorder_group = Mental.Health.Disorder.Group, 
         description = Description, 
         originalCode = ICD10_Code) %>%
  mutate( ICD10_Code= ifelse( nchar( originalCode) > 3, paste0(substr( originalCode, 1, 3), ".", substr(  originalCode, 4, nchar(originalCode))),originalCode)) %>%
  select( disorder_group, ICD10_Code, description)
```

>>>>

```{r}
#icdCodes <- read.csv("public-data/pediatric_psychiatric_ICD10_codes.csv", header = TRUE, colClasses = "character") %>% 
#  rename(disorder_group = Mental.Health.Disorder.Group, 
#         description = Description, 
#         originalCode = ICD10_Code) %>%
#  mutate( ICD10_Code= ifelse( nchar( originalCode) > 3, paste0(substr( originalCode, 1, 3), ".", substr(  originalCode, 4, nchar(originalCode))),originalCode)) %>%
#  select( disorder_group, ICD10_Code, description)

icdCodes <- read.csv("public-data/pediatric_psychiatric_ICD10_codesV2.csv", header = TRUE, colClasses = "character") %>%
   filter( flag %in% c("originalCodes", "FrenchSpecificCodes")) %>%
   select( disorder_group, ICD10_Code, description )
```
